The Astropy Project

### 2017-12-08 main.tex
Edits from Sections 3.8 to 6, inclusive

\subsection{Astropy development model}
% draft by Adrian PW and Erik T.
Code is contributed to the \astropypkg core package or modified through ``pull
requests'' (via \github) that often contain several \texttt{git} commits.
Pull requests may fix bugs, implement new features, or improve or modify the
infrastructure that supports the development and maintenance of the package.
Individual pull requests are generally limited to a single conceptual addition
or modification to make code review tractable.
Pull requests that modify or add code to a specific subpackage must be reviewed
and approved by one of the subpackage maintainers before it is merged into the
core codebase.
Bugs and feature requests are reported via the \github issue tracker and labeled
with a set of possible labels that help classify and organize the issues.
The development workflow is detailed in the \astropypkg
documentation.\footnote{\emph{How to make a code contribution},
\url{http://docs.astropy.org/en/latest/development/workflow/development_workflow.html}}

@@

The released versions of the \astropypkg core package are available from several
of the \python distributions for scientific computing (e.g.,
\href{http://anaconda.org}{Anaconda}) and from the \python Package Index
(PyPI).\footnote{See the installation documentation for more information:
\url{http://docs.astropy.org/en/stable/install.html}}
Effort has been made to make \astropypkg available and easily installable across
all platforms; the package is constantly tested on different platforms as part
of a suite of continuous integration tests.

@@

\section{Astropy Core Package version 2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing
astronomical files, and units) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version 0.2 (previously described in \citealt{astropy}).  The \astropypkg
package
provides a full log of changes\footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
over the course of the entire project and more details about individual
subpackages are available in the documentation.\footnote{\url{http://docs.astropy.org/en/stable/}}
Beyond what is mentioned below, most subpackages have seen increased performance
since the release of the version 0.2 package.

@@

The \texttt{NDDataBase} class provides the abstract interface for gridded data
with attributes for accessing metadata, the world-coordinate system (WCS),
uncertainty arrays matched to the shape of the data, and other traits.
Building on this interface, the \texttt{NDData} class provides a minimal
working implementation for storing \package{numpy} arrays. These classes serve
as useful base classes for package authors wishing to develop their own classes
for specific use cases and as containers for exchanging gridded data.

@@

The \package{astropy.convolution} subpackage implements
``normalized convolution'' \citep[e.g.,][]{Knutsson1993}, which is an image
reconstruction technique in which missing data are ignored during the
convolution and replaced with values interpolated using the kernel.
An example of this is given in \figurename~\ref{fig:convolution-example}.
In versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT)
convolution approaches were not consistent, with FFT convolution implementing
normalized convolution and direct convolution implementing a different approach.
As of version 2.0, the two methods are consistent and include a suite of
consistency checks.

@@

The \package{astropy.visualization} subpackage provides functionality that can
be helpful when visualizing data. This includes a framework for plotting
astronomical images with coordinates with \package{matplotlib} (previously the
standalone \package{wcsaxes} package), functionality related to image
normalization (including both scaling and stretching), smart histogram
plotting, RGB color image creation from separate images, and custom plotting
styles for \package{matplotlib}.

@@

Normalization transforms the images values to the range $[0,1]$ using lower and
upper limits $(v_{\rm min}, v_{\rm max})$
\begin{equation}
y = \frac{x - v_{\rm min}}{v_{\rm max} - v_{\rm min}}
\end{equation}
where $x$ represents the values in the original image.

Stretching transforms the image values in the range $[0,1]$ again to the range
$[0,1]$ using a linear or non-linear function
\begin{equation}
z = f(y) \quad .
\end{equation}

@@

\package{matplotlib} allows a custom normalization and stretch to be used when
displaying data by passing a normalization object.
The \package{astropy.visualization} package also provides a normalization class
that wraps the interval and stretching objects into a normalization object that
\package{matplotlib} understands.

@@

Astronomers dealing with observational imaging commonly need to make figures
with images that include the correct coordinates and optionally display a
coordinate grid. The challenge, however, is that the conceptual coordinate axes
(such as longitude/latitude) need not be lined up with the pixel axes of the
image. The \package{astropy.visualization.wcsaxes} subpackage implements a
generalized way of making figures from an image array and a world coordinate
system (WCS) object that provides the transformation between pixel and
``world'' coordinates.

World coordinates can be, for example, right ascension and declination, but can
also include, for example, velocity, wavelength, frequency, or time.
The main features from this subpackage include the ability to control which
axes to show which coordinate on (for example showing longitude ticks on the
top and bottom axes and latitude on the left and right axes), controlling the
spacing of the ticks either by specifying the positions to use or providing a
tick spacing or an average number of ticks that should be present on each axis,
setting the format for the tick labels to ones commonly used by astronomers,
controlling the visibility of the grid/graticule, and overlaying ticks, labels,
and/or grid lines from different coordinate systems. In addition, it is
possible to pass data with more than two dimensions and slice on-the-fly.
Finally, it is possible to define non-rectangular frames, such as, for example,
Aitoff projections.

This subpackage differs from \package{APLpy} \citep{aplpy} in that the latter
focuses on providing a very high-level interface to plotting that requires very
few lines of code to get a good result, whereas \package{wcsaxes} defines an
interface that is much closer to that of \package{matplotlib} \citep{matplotlib}.
This enables significantly more advanced visualizations.

An example of a visualization made with \package{wcsaxes} is shown in
\figurename~\ref{fig:wcsaxes} -- this example illustrates the ability to
overlay multiple coordinate systems and customize which ticks/labels are shown
on which axes around the image. This also uses the image stretching
functionality from \sectionname~\ref{sec:stretch} to show the image in a square
root stretch (automatically updating the tick positions in the colorbar).

@@

\package{astropy.visualization} also provides a histogram function, which is a
generalization of \texttt{matplotlib}’s histogram function, to allow for more
flexible specification of histogram bins.  The function provides several methods
of automatically tuning the histogram bin size. It has a syntax identical to
\texttt{matplotlib}’s histogram function, with the exception of the \texttt{bins}
parameter, which allows specification of one of four different methods for
automatic bin selection: `blocks', `knuth', `scott', or `freedman'.

@@

\cite{Lupton2004} describe an ``optimal'' algorithm for producing
red-green-blue (RGB) composite images from three separate high-dynamic range
arrays. The \package{astropy.visualization} subpackage provides a convenience
function to create such a color image.  It also includes an associated set of
classes to provide alternate scalings.
This functionality was contributed by developers from the Large Synoptic Survey
Telescope (LSST) and serves as an example of contribution to \astropy from a
more traditional engineering organization \citep{Jennes2016}.

The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a
variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977}
we show an RGB color image of the Hickson 88 group, centered near NGC~6977.
This image was generated from SDSS images using the
\package{astropy.visualization} tools.

@@

The \package{astropy.stats} package provides statistical tools that
are useful for or specific to astronomy and are not found in or extend
the available functionality of other \python statistics packages such
as \package{scipy} \citep{scipy} or \package{statsmodels}
\citep{seabold2010statsmodels}.  \package{astropy.stats} contains
a range of functionality used by many different disciplines
in astronomy. It is not a complete set of statistic tools, but rather
a still growing collection of useful features.

@@

Astronomers often need to compute statistics of quantities evaluated on a circle, such as sky direction or polarization angle.
A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
are implemented in \package{astropy.stats}.  These functions provide
measurements of the circular mean, variance, and moment.   For all of these
functions, they work with both \texttt{numpy.ndarrays} (assumed to be in
radians) and \texttt{Quantity} objects.  In addition, the subpackage includes
tests for Rayleigh Test, vtest, and a function to compute the maximum likelihood
estimator for the parameters of the von Mises distribution.

@@

Periodic analysis of unevenly-spaced time series is common across many subfields of astronomy. The \package{astropy.stats} package now includes several efficient implementations of the Lomb-Scargle periodogram \citep{Lomb76, Scargle82} and several generalizations, including floating mean models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003}, and appropriate handling of heteroscedastic uncertainties. Importantly, the implementations make use of several fast and scalable computational approaches \citep[e.g.,][]{Press89, Palmer09}, and so can be applied to much larger datasets than Lomb-Scargle algorithms available in, e.g., \package{scipy.stats} (\citealt{scipy}). Much of the Lomb-Scargle code in \astropypkg has been adapted from previously-published open-source code \citep{astroML, VanderPlas2015}.

\subsubsection{Bayesian Blocks and Histogram Binning}
\astropypkg also includes an implementation of {\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of break-points in non-periodic astronomical time-series. One interesting application of Bayesian Blocks is its use in determining optimal histogram binnings, and in particular binnings with unequal bin sizes. This code was adapted, with several improvements, from the \package{astroML} package \citep{astroML}. An example of a histogram fit using the Bayesian blocks algorithm is shown in the right panel of \figurename~\ref{fig:bayes-blocks-hist}.

@@

In addition to astronomy-specific packages and libraries, the \astropy Project
also maintains and distributes several general-purpose infrastructure packages
that help with the maintenance and upkeep of the \astropypkg core package and
other affiliated packages.
The following sections describes the most widely-used infrastructure packages
developed by the \astropy Project.

@@

\astropy also provides a set of scripts for setting up and configuring
continuous integration (CI) services as a \github repository,
\package{astropy/ci-helpers}.\footnote{\url{https://github.com/astropy/ci-helpers}}
These tools aim to empower package maintainers to control their testing set up
and installation process for various continuous integration services through a
set of environment variables.
While the current development is mostly driven by the needs of the \astropy
ecosystem, the actual usage of this package is extremely widespread. The current
tools support configuration for Travis CI and Appveyor CI.

@@

The documentation for many \python packages, the core \astropypkg package, and
for all packages in the \astropy ecosystem is written using the
\package{Sphinx} documentation build system.
\package{Sphinx} makes it possible to write documentation using plain text files
that follow a markup language called ``reStructuredText,'' which are then
transformed into HTML or \LaTeX{} documentation during the documentation build
process.
For the \astropy project, we have developed a few \package{Sphinx} extensions
that facilitate automatically generating API documentation for large projects,
like the \astropypkg core package.
The main extension we have developed is
\package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}},
which makes it easy with a single reStructuredText command to generate a set of
documentation pages listing all of the available classes, functions, and
attributes in a given \python module.

@@

Following the release of version 2.0, development on the next major version of
the \astropypkg core package (version 3.0) has already begun.
On top of planned changes and additions to the core package, we also plan to
overhaul the \astropy educational and learning materials, and further refactor
and generalize the infrastructure utilities developed for the core package for
the benefit of the community.

@@

One of the most significant changes coming in this next major release will be
removing support for \python 2 \citep{ape10}: future versions of \astropypkg
will only support \python 3.5 and higher.
Removing \python 2 support will allow the use of new, \python 3-only features,
will simplify the code base, and reduce the testing overhead for the package.
\astropypkg version 3.0 is currently scheduled for January 2018.

In the next major release after version 3.0, scheduled for
mid-2018, the focus will be on optimization of the code and improved
documentation.
To prepare for this release, we are preparing software for testing, evaluating,
and monitoring the performance of the code.
Less functionality may be introduced in this release while the focus will be
primarily on improved performance.

Beyond the core code, the \astropy project is also further developing the
\astropy-managed affiliated packages.
While these may not be integrated into the \astropypkg core package, these
projects provide code that is useful to the astronomical community and meet the
testing and documentation standards of \astropy.
Some of these new efforts includes an initiative to develop tools for
spectroscopy \citep[\package{specutils}, \package{specreduc}, \package{specviz}]
{ape13}, integration of LSST software, and packages to support HEALPIX
projection. %\citep{astropy-healpix}
%\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}

@@

The \astropypkg core package documentation contains narrative descriptions of
the package functionality along with detailed usage notes for functions,
classes, and modules.
While useful as a reference and for more advanced \python users, it is not the
right entry-point for all users or learning environments.
In the near future, we will launch a new resource for learning to use both the
\astropypkg core package and the many packages in the broader \astropy
ecosystem, under the name `\emph{Learn Astropy}.'

The new \emph{Learn Astropy} site will present several different ways to engage
with the \astropy ecosystem:
\begin{description}
    \item[Documentation] The \astropypkg and affiliated package documentation
        contain the complete description of a package with all requisite
        details, including usage, dependencies, and examples.
        The pages will largely remain as-is, but will be focused towards more
        intermediate users and as a reference resource.
    \item[Examples] These are stand-alone code snippets that live in the
        \astropypkg documentation that demonstrate a specific functionality
        within a subpackage.
        The \astropypkg core package documentation will then gain a new ``index
        of examples'' that links to all of the code or demonstrative examples
        within any documentation page.
    \item[Tutorials] The \astropy tutorials are step-by-step demonstrations of
        common tasks that incorporate several packages or subpackages.
        Tutorials are more extended and comprehensive than examples, may contain
        exercises for the users, and are generally geared towards workshops or
        teaching.
        Several tutorials already
        exist\footnote{\url{http://tutorials.astropy.org/}} and are being
        actively expanded.
    \item[Guides] These are long-form narrative, comprehensive,
        conceptually-focused documents (roughly one book chapter in length)
        providing stand-alone introductions to core packages in addition to the
        underlying astronomical concepts.
        These are less specific and more conceptual than tutorials.
        For example, ``using \astropypkg and \package{ccdproc} to reduce imaging
        data.''
\end{description}
We encourage any users who wish to see specific material to either contribute or
comment on these efforts via the \astropy mailing list or \package{astropy/astropy-tutorials}
\github repository.\footnote{\url{https://github.com/astropy/astropy-tutorials}}

@@

The development of the \astropypkg package and cultivation of the \astropy
ecosystem is still maintaining significant growth while improving stability,
breadth, and reliability.
As the \astropypkg core package becomes more mature, several subpackages have
reached stability with a rich set of features that help astronomers worldwide to
perform many daily tasks such as planning observations, analyzing data or
simulation results, and writing publications.
The strong emphasis that the \astropy project puts on reliability and code
correctness helps users to trust the calculations performed with \astropypkg and
to publish reproducible results.
At the same time, the \astropy ecosystem and core package are growing: new
functionality is still being contributed, and new affiliated packages are being
developed to support more specialized needs.

The \astropy project is also spreading awareness of best practices in
community-driven software development.
This is important as most practicing astronomers were not explicitly taught
computer science and software development, despite the fact that a major
fraction of nearly every astronomer's workload today is related to software use
and development.
The \astropypkg package leads by example, showing all interested astronomers how
modern tools like \texttt{git} version control or continuous integration can
increase the quality, accessibility, and discoverability of astronomical
software without overly complicating the development cycle.
Within \astropy, all submitted code is reviewed by at least one, but typically
more, members of the \astropy community, who provide feedback to contributors
to help improve their skills.
As a community, \astropy follows an explicit code of conduct \citep{ape8} and treats all
contributors and users with respect, provides a harassment-free environment, and
encourages and welcomes new contributions from all.
Thus, while the \astropy project provides and develops software and tools
essential to modern astronomical research, it also helps to prepare the current
and next generation of researchers with the knowledge to adequately use,
develop, and contribute to those tools within a conscientious and welcoming
community.

>>>>

\subsection{Astropy development model}
% draft by Adrian PW and Erik T.
code is contributed to the \astropypkg core package or modified through ``pull
requests'' (via \github) that often contain several \texttt{git} commits.
Pull requests may fix bugs, implement new features, or improve or modify the
infrastructure that supports the development and maintenance of the package.
Individual pull requests are generally limited to a single conceptual addition
or modification to make code review tractable.
Pull requests that modify or add code to a specific subpackage must be reviewed
and approved by one of the subpackage maintainers before it is merged into the
core codebase.
Bugs and feature requests are reported via the \github issue tracker and labeled
with a set of possible labels that help classify and organize the issues.
The development workflow is detailed in the \astropypkg
documentation.\footnote{\emph{How to make a code contribution},
\url{http://docs.astropy.org/en/latest/development/workflow/development_workflow.html}}

@@

The released versions of the \astropypkg core package are available from several
of the \python distributions for scientific computing (e.g.,
\href{http://anaconda.org}{Anaconda}) and from the \python Package Index
(PyPI).\footnote{See the installation documentation for more information:
\url{http://docs.astropy.org/en/stable/install.html}}
Effort has been made to make \astropypkg available and easily installable across
all platforms; the package is constantly tested on different platforms as part
of a suite of continuous integration (CI) tests.

@@

%\subsection{Difficulty of reversing design choices}
%Deciding if a feature should be included
%difficulty to decide where general use ends and "handy feature for some" starts, i.e. how to reject PRs or deal with maintenance burden

\section{Astropy Core Package Version 2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing
astronomical files, and units) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version 0.2 (previously described in \citealt{astropy}).  The \astropypkg
package
provides a full log of changes\footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
over the course of the entire project and more details about individual
subpackages are available in the documentation.\footnote{\url{http://docs.astropy.org/en/stable/}}
Beyond what is mentioned below, most subpackages have seen increased performance
since the release of the version 0.2 package.

@@

The \texttt{NDDataBase} class provides the abstract interface for gridded data
with attributes for accessing metadata, the world coordinate system (WCS),
uncertainty arrays matched to the shape of the data, and other traits.
Building on this interface, the \texttt{NDData} class provides a minimal
working implementation for storing \package{numpy} arrays. These classes serve
as useful base classes for package authors wishing to develop their own classes
for specific use cases and as containers for exchanging gridded data.

@@

The \package{astropy.convolution} subpackage implements
``normalized convolution'' \citep[e.g.,][]{Knutsson1993} that is an image
reconstruction technique, in which missing data are ignored during the
convolution and replaced with values interpolated using the kernel;
An example of this is given in \figurename~\ref{fig:convolution-example}.
In \astropypkg versions $\leq 1.3$, the direct convolution and Fast Fourier Transform (FFT)
convolution approaches were inconsistent, with the latter implementing
normalized convolution, while the former a different approach.
As of version 2.0, the two methods now agree and include a suite of
consistency checks.

@@

The \package{astropy.visualization} subpackage provides functionality that can
be helpful when visualizing data. This includes a framework (previously the
standalone \package{wcsaxes} package) for plotting
astronomical images with coordinates with \package{matplotlib}, functionality related to image
normalization (including both scaling and stretching), smart histogram
plotting, red-green-blue (RGB) color image creation from separate images,
and custom plotting styles for \package{matplotlib}.

@@

Normalization transforms the image values to the range $[0,1]$ using lower and
upper limits $(v_{\rm min}, v_{\rm max})$,
\begin{equation}
y = \frac{x - v_{\rm min}}{v_{\rm max} - v_{\rm min}} \quad ,
\end{equation}
where $x$ represents the values in the original image.

Stretching transforms the image values in the range $[0,1]$ again to the range
$[0,1]$ using a linear or non-linear function,
\begin{equation}
z = f(y) \quad .
\end{equation}

@@

\package{matplotlib} allows a custom normalization and stretch to be used when
displaying data by passing in a normalization object.
The \package{astropy.visualization} package also provides a normalization class
that wraps the interval and stretches objects into a normalization object that
\package{matplotlib} understands.

@@

Astronomers dealing with observational imaging commonly need to make figures
with images that include the correct coordinates and optionally display a
coordinate grid. The challenge, however, is that the conceptual coordinate axes
(such as longitude/latitude) need not be lined up with the pixel axes of the
image. The \package{astropy.visualization.wcsaxes} subpackage implements a
generalized way of making figures from an image array and a world coordinate
system (WCS) object that provides the transformation between pixel and
world coordinates.

World coordinates can be, for example, right ascension and declination, but can
also include, for example, velocity, wavelength, frequency, or time.
The main features from this subpackage include the ability to control which
axes to show which coordinate on (e.g., showing longitude ticks on the
top and bottom axes and latitude on the left and right axes), controlling the
spacing of the ticks either by specifying the positions to use or providing a
tick spacing or an average number of ticks that should be present on each axis,
setting the format for the tick labels to ones commonly used by astronomers,
controlling the visibility of the grid/graticule, and overlaying ticks, labels,
and/or grid lines from different coordinate systems. In addition, it is
possible to pass data with more than two dimensions and slice on-the-fly.
Last but not least, it is also able to define non-rectangular frames, such as,
for example, Aitoff projections.

This subpackage differs from \package{APLpy} \citep{aplpy}, in that the latter
focuses on providing a very high-level interface to plotting that requires very
few lines of code to get a good result, whereas \package{wcsaxes} defines an
interface that is much closer to that of \package{matplotlib} \citep{matplotlib}.
This enables significantly more advanced visualizations.

An example of a visualization made with \package{wcsaxes} is shown in
\figurename~\ref{fig:wcsaxes}; This example illustrates the ability to
overlay multiple coordinate systems and customize which ticks/labels are shown
on which axes around the image. This also uses the image stretching
functionality from \sectionname~\ref{sec:stretch} to show the image in a
square-root stretch (automatically updating the tick positions in the colorbar).

@@

\package{astropy.visualization} also provides a histogram function, which is a
generalization of \texttt{matplotlib}’s histogram function, to allow for a more
flexible specification of histogram bins.  The function provides several methods
of automatically tuning the histogram bin size. It has a syntax identical to
\texttt{matplotlib}’s histogram function, with the exception of the \texttt{bins}
parameter, which allows specification of one of four different methods for
automatic bin selection: ``blocks'', ``knuth'', ``scott'', or ``freedman''.

@@

\cite{Lupton2004} describe an ``optimal'' algorithm for producing
RGB composite images from three separate high-dynamic range
arrays. The \package{astropy.visualization} subpackage provides a convenience
function to create such a color image.  It also includes an associated set of
classes to provide alternate scalings.
This functionality was contributed by developers from the Large Synoptic Survey
Telescope (LSST) and serves as an example of contribution to \astropy from a
more traditional engineering organization \citep{Jennes2016}.

The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a
variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977},
we show an RGB color image of the Hickson 88 group, centered near NGC~6977.
This image was generated from SDSS images using the
\package{astropy.visualization} tools.

@@

The \package{astropy.stats} package provides statistical tools that
are useful for astronomy and are either not found in or extend
the available functionality of other \python statistics packages, such
as \package{scipy} \citep{scipy} or \package{statsmodels}
\citep{seabold2010statsmodels}.  \package{astropy.stats} contains
a range of functionality used by many different disciplines
in astronomy. It is not a complete set of statistical tools, but rather
a still growing collection of useful features.

@@

Astronomers often need to compute statistics of quantities evaluated on a
circle, such as sky direction or polarization angle.
A set of circular statistical estimators based on \citet{JammalamadakaSengupta}
are implemented in \package{astropy.stats}.  These functions provide
measurements of the circular mean, variance, and moment.   For all of these
functions, they work with both \texttt{numpy.ndarrays} (assumed to be in
radians) and \texttt{Quantity} objects.  In addition, the subpackage includes
tests for Rayleigh Test, \texttt{vtest}, and a function to compute the maximum
likelihood estimator for the parameters of the von Mises distribution.

@@

Periodic analysis of unevenly-spaced time series is common across many
sub-fields of astronomy. The \package{astropy.stats} package now includes
several efficient implementations of the Lomb-Scargle periodogram
\citep{Lomb76, Scargle82} and several generalizations, including floating mean
models \citep{Zechmeister09}, truncated Fourier models \citep{Bretthorst2003},
and appropriate handling of heteroscedastic uncertainties.
Importantly, the implementations make use of several fast and scalable
computational approaches \citep[e.g.,][]{Press89, Palmer09}, and thus can be
applied to much larger datasets than Lomb-Scargle algorithms available in,
e.g., \package{scipy.stats} (\citealt{scipy}). Much of the Lomb-Scargle code
in \astropypkg has been adapted from previously-published open-source code
\citep{astroML, VanderPlas2015}.

\subsubsection{Bayesian Blocks and Histogram Binning}
\package{astropy.stats} also includes an implementation of
{\it Bayesian Blocks} \citep{Scargle2013}, an algorithm for analysis of
break-points in non-periodic astronomical time-series. One interesting
application of Bayesian Blocks is its use in determining optimal histogram
binnings, particularly binnings with unequal bin sizes.
This code was adapted, with several improvements, from the \package{astroML}
package \citep{astroML}. An example of a histogram fit using the Bayesian
Blocks algorithm is shown in the right panel of
\figurename~\ref{fig:bayes-blocks-hist}.

@@

In addition to astronomy-specific packages and libraries, the \astropy Project
also maintains and distributes several general-purpose infrastructure packages
that assist the maintenance and upkeep of the \astropypkg core package and
other affiliated packages.
The following sections describe the most widely-used infrastructure packages
developed by the \astropy Project.

@@

\astropy also provides a set of scripts for setting up and configuring
CI services as a \github repository,
\package{astropy/ci-helpers}.\footnote{\url{https://github.com/astropy/ci-helpers}}
These tools aim to empower package maintainers to control their testing setup
and installation process for various CI services through a
set of environment variables.
While the current development is mostly driven by the needs of the \astropy
ecosystem, the actual usage of this package is extremely widespread. The current
tools support configuration for Travis CI and Appveyor CI.

@@

The documentation for many \python packages, including
all the packages in the \astropy ecosystem, is written using the
\package{Sphinx} documentation build system.
\package{Sphinx} supports writing documentation using plain text files
that follow a markup language called \texttt{reStructuredText} (RST).
These files are then transformed into HTML, PDF, or \LaTeX{} documents
during the documentation build process.
For the \astropy project, we have developed several \package{Sphinx} extensions
that facilitate automatically generating API documentation for large projects,
like the \astropypkg core package.
The main extension we have developed is
\package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}},
which provides a convenient single RST command to generate a set of
documentation pages, listing all of the available classes, functions, and
attributes in a given \python module.

@@

Following the release of version 2.0, development on the next major version of
the \astropypkg core package (version 3.0) has already begun.
On top of planned changes and additions to the core package, we also plan to
overhaul the \astropy educational/learning materials and further
generalize the infrastructure utilities originally developed for the core
package for the benefit of the community.

@@

One of the most significant changes coming in this next major release will be
removing the support for \python 2 \citep{ape10}: future versions of \astropypkg
will only support \python 3.5 or higher.
Removing \python 2 support will allow the use of new \python 3-only features,
simplify the code base, and reduce the testing overhead for the package.
\astropypkg version 3.0 is currently scheduled for January 2018.

In the next major release after version 3.0, scheduled for
mid-2018, the focus will be on algorithm optimization and
documentation improvement.
To prepare for this release, we are subjecting the core package to testing,
evaluation, and performance monitoring.
As a result, less new functionality may be introduced as a trade-off for
better performance.

Beyond the core code, the \astropy project is also further developing the
\astropy-managed affiliated packages.
While these may not be integrated into the \astropypkg core package, these
projects provide code that are useful to the astronomical community and meet the
testing and documentation standards of \astropy.
Some of these new efforts include an initiative to develop tools for
spectroscopy \citep[\package{specutils}, \package{specreduc}, \package{specviz}]
{ape13}, integration of LSST software, and support for HEALPIX
projection. %\citep{astropy-healpix}
%\inlinecomment{BMS}{TODO: uncomment references of packages once they are available}

@@

The \astropypkg core package's documentation contains narrative descriptions of
the package's functionality, along with detailed usage notes for functions,
classes, and modules.
While useful as a reference for more experienced \python users, it is not the
proper entry-point for other users or learning environments.
In the near future, we will launch a new resource for learning to use both the
\astropypkg core package and the many packages in the broader \astropy
ecosystem, under the name \emph{Learn Astropy}.

The new \emph{Learn Astropy} site will present several different ways to engage
with the \astropy ecosystem:
\begin{description}
    \item[Documentation] The \astropypkg and affiliated package documentation
        contains the complete description of a package with all requisite
        details, including usage, dependencies, and examples.
        The pages will largely remain as-is, but will be focused towards more
        intermediate users and as a reference resource.
    \item[Examples] These are stand-alone code snippets that live in the
        \astropypkg documentation that demonstrate a specific functionality
        within a subpackage.
        The \astropypkg core package documentation will then gain a new ``index
        of examples'' that links to all of the code or demonstrative examples
        within any documentation page.
    \item[Tutorials] The \astropy tutorials are step-by-step demonstrations of
        common tasks that incorporate several packages or subpackages.
        Tutorials are more extended and comprehensive than examples, may contain
        exercises for the users, and are generally geared towards pedagogical
        activities.
        Several tutorials already
        exist\footnote{\url{http://tutorials.astropy.org/}} and are being
        actively expanded.
    \item[Guides] These are long-form narrative, comprehensive, and
        conceptually-focused documents (roughly one book chapter in length),
        providing stand-alone introductions to core packages in addition to the
        underlying astronomical concepts.
        These are less specific and more conceptual than tutorials;
        For example, ``using \astropypkg and \package{ccdproc} to reduce imaging
        data.''
\end{description}
We encourage any users who wish to see specific material to either contribute or
comment on these efforts via the \astropy mailing list or \package{astropy/astropy-tutorials}
\github repository.\footnote{\url{https://github.com/astropy/astropy-tutorials}}

@@

The development of the \astropypkg package and cultivation of the \astropy
ecosystem are still maintaining significant growth while improving in stability,
breadth, and reliability.
As the \astropypkg core package becomes more mature, several subpackages have
reached stability with a rich set of features that help astronomers worldwide to
perform many daily tasks, such as planning observations, analyzing data or
simulation results, and writing publications.
The strong emphasis that the \astropy project puts on reliability and high coding
standards helps users to trust the calculations performed with \astropypkg and
to publish reproducible results.
At the same time, the \astropy ecosystem and core package are both growing: new
functionality is still being contributed and new affiliated packages are being
developed to support more specialized needs.

The \astropy project is also spreading awareness of best practices in
community-driven software development.
This is important as most practicing astronomers were not explicitly taught
computer science and software development, despite the fact that a major
fraction of many astronomers' workload today is related to software use
and development.
The \astropypkg package leads by example, showing all interested astronomers how
modern tools like \texttt{git} version control or CI testing can
increase the quality, accessibility, and discoverability of astronomical
software without overly complicating the development cycle.
Within \astropy, all submitted code is reviewed by at least one, but typically
more, members of the \astropy community, who provide feedback to contributors
to help improve their skills.
As a community, \astropy follows an explicit code of conduct \citep{ape8} and treats all
contributors and users with respect, provides a harassment-free environment, and
encourages and welcomes new contributions from all.
Thus, while the \astropy project provides and develops software and tools
essential to modern astronomical research, it also helps to prepare the current
and next generation of researchers with the knowledge to adequately use,
develop, and contribute to those tools within a conscientious and welcoming
community.
